Analyzing Fairness: Race, Recidivism, and the COMPAS Algorithm

### 2022-04-18 final_metrics_analysis.Rmd
amrita's changes

```{r py setup, include=FALSE}
library(reticulate)

# for Dianne
use_condaenv("base")

# for Amrita
# use_condaenv("anaconda3")
```

@@

```{python make degree numeric}
#av_defendant = (df_viz.groupby(['race'],as_index=False).age.mean()
#display(df_viz)
#list_vars = list(df_viz)
#list_vars
#df_numeric_charges = df_viz['c_charge_degree'].replace(['M', 'F'], [0, 1], inplace=True)
#plt.bar('c_charge_degree', 1, data = df_viz)
```

@@

```{python exploratory age by race plot}
# age distribution by race
ax = sns.kdeplot(x="age", hue="race", data=df_viz, palette=workshop_palette);
kdeline = ax.lines[0]
mean_black = df_viz.groupby('race').age.median()[0]
xs = kdeline.get_xdata()
ys = kdeline.get_ydata()
height_black = np.interp(mean_black, xs, ys)
ax.vlines(mean_black, 0, height_black, color=purple, ls=':')

mean_white = df_viz.groupby('race').age.median()[1]
height_white = np.interp(mean_white, xs, ys)
ax.vlines(mean_white, 0, height_white, color=green, ls=':')

print(df_viz.groupby('race').age.median())

plt.title('Distribution of Age by Race')
```

@@

```{python post-processing calibrated equal odds set up, include = FALSE}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta

@@

>>>>

```{r py setup, include=FALSE}
library(reticulate)
use_condaenv("anaconda3")
```

@@

@@

```{python exploratory age by race plot}
# age distribution by race
#ax = sns.kdeplot(x="age", hue="race", data=df_viz, palette=workshop_palette);
#kdeline = ax.lines[0]
#mean_black = df_viz.groupby('race').age.median()[0]
#xs = kdeline.get_xdata()
#ys = kdeline.get_ydata()
#height_black = np.interp(mean_black, xs, ys)
#ax.vlines(mean_black, 0, height_black, color=purple, ls=':')

#mean_white = df_viz.groupby('race').age.median()[1]
#height_white = np.interp(mean_white, xs, ys)
#ax.vlines(mean_white, 0, height_white, color=green, ls=':')

#print(df_viz.groupby('race').age.median())

#plt.title('Distribution of Age by Race')
```

@@

```{python post-processing calibrated equal odds set up, include = FALSE}
from aif360.algorithms.postprocessing import EqOddsPostprocessing
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta

@@

```{python} 
ep = EqOddsPostprocessing(unprivileged_groups=0, privileged_groups= 1, seed =1234567)
eo = PostProcessingMeta(estimator=lr, postprocessor=ep, random_state=1234567)
eo.fit(train_BLD, test_BLD)
y_pred_EO = eo.predict(test_BLD)
#y_proba_EO = eo.predict_(test_BLD)

```
